 Group Report

### 2024-12-09 draft.Rmd
Update draft.Rmd

```{r include = FALSE}
#split data
set.seed(20)
data <- 
    data %>% 
    mutate(id = row_number())

@@

### Results

#### Coefficient Significance ($\alpha$ = 0.05) / Confidence Intervals $(95\%)$

-   **Intercept**: $\beta_0$ ( [8.23, 10.9] )

    We reject $H_0$ since the $p-value$ is $8.33 \times 10^{-32}$. This
    indicates that the intercept is statistically significant,
    suggesting that the baseline levels of the predictors have a
    meaningful contribution to the average student performance.

    Besides that we are 95% confident that the true value of the
    intercept lies within $[8.23, 10.9]$. Since the range is entirely >
    1, it also suggests that the baseline group is associated with
    higher levels of student performance compared to other predictor
    categories.

-   **School**: $\beta_1$ ( [-2.09, -0.741] )

    The $p-value$ $5.35 \times10^{-5}$ is less than $0.05$, so we reject
    $H_0$. This result indicates that the type of school is
    significantly associated with average student performance.

@@

-   **Medu**: $\beta_2$ ( [-0.0659, 0.496] )

    The $p-value$ $1.33 \times 10^{-1}$ is greater than $0.05$, so we
    fail to reject $H_0$. There is insufficient evidence to conclude
    that mother's education level is significantly associated with
    average student performance.

    The confidence interval includes 0, also indicates no significant
    evidence to conclude a relationship between mother's education level
    (Medu) and higher student performance.

-   **Higher**: $\beta_3$ ( [1.33, 3.48] )

    The $p-value$ $1.82 \times 10^{-5}$ is less than $0.05$, so we
    reject $H_0$. This suggests that planning to pursue higher education
    is significantly associated with improved average student
    performance.

    We can see the range $[1.33, 3.48]$ lies entirely > 1, also suggests
    a significant positive relationship between planning to pursue
    higher education degree and better student performance.

-   **Absences**: $\beta_4$ ( [-0.199, -0.0629] )

    The $p-value$ = $2.01\times 10^{-4}$ is less than $0.05$, so we reject
    $H_0$. This indicates that absences are significantly associated
    with lower average student performance.

@@

In conclusion, although our model provides statistical significant
results for all four predictors, the low $R^2$ value of 0.289 suggests
that there might be other predictor variables influencing
log(G1_G2_Average) that are not captured in our analysis. Further
exploration and analysis of the predictor variables in the future may
help with defining these relationships.

## IV. Appendix

```{r}
null_model <- lm(G1_G2_Average ~ 1, data = testing_data)
selected_model <- lm(G1_G2_Average ~ school + Medu + higher + absences, data = testing_data)
```

```{r}
AIC(null_model, selected_model)
```

### References

>>>>

```{r include = FALSE}
#split data
set.seed(11)
data <- 
    data %>% 
    mutate(id = row_number())

@@

### Results
#### Coefficient Significance $(α = 0.05)$ / Confidence Intervals $(95\%)$
- **Intercept**: $\beta_0\$ \( [8.97, 11.4] \)

   We reject $H_0$ since the $p-value$ is $3.41 \times 10^{-38}$. This indicates that the intercept is statistically significant, suggesting that the baseline levels of the predictors have a meaningful contribution to the average student performance.

   Besides that we are 95% confident that the true value of the intercept lies within $[8.97, 11.4]$. Since the range is entirely > 1, it also suggests that the baseline group is associated with higher levels of student performance compared to other predictor categories.

- **School**: $\beta_1\$ \( [-2.58, -1.15] \)

  The $p-value$ $6.40 \times 10^{-7}$ is less than $0.05$, so we reject $H_0$. This result indicates that the type of school is significantly associated with average student performance.

@@

- **Medu**: $\beta_2\$ \( [0.0418, 0.632] \)

  The $p-value$ $2.55 \times 10^{-2}$ is less than $0.05$, so we reject $H_0$. There is enough evidence to conclude that mother's education level is significantly associated with average student performance.

  The confidence interval didn't includes 0, also indicates evidence to conclude a relationship between mother’s education level (Medu) and higher student performance.

- **Higher**: $\beta_3\$ \( [0.826, 2.93] \)

  The $p-value$ $5.42 \times 10^{-4}$ is less than $0.05$, so we reject $H_0$. This suggests that planning to pursue higher education is significantly associated with improved average student performance.

  We can see the range $[0.826, 2.93]$ lies entirely > 0, also suggests a significant positive relationship between planning to pursue higher education degree and better student performance.

- **Absences**: $\beta_4\$ \( [-0.152, -0.0152] \)

  The $p-value$ $1.68 \times 10^{-2}$ is less than $0.05$, so we reject $H_0$. This indicates that absences are significantly associated with lower average student performance.

@@

In conclusion, although our model provides statistical significant
results for all four predictors, the low $R^2$ value of 0.259 suggests
that there might be other predictor variables influencing
log(G1_G2_Average) that are not captured in our analysis. Further
exploration and analysis of the predictor variables in the future may
help with defining these relationships.

## IV. Appendix
### References
